Ceph Parallel File System Evaluation Report

### 2013-11-11 baseline.tex
minor fix
minor fixes for final touch

The lowest layer in the system are the exposed LUNs to the server hosts from
the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
disks and 2 \textit{P} and \textit{Q} disks). In prior tests we observed
that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
For these tests, all disk caches were turned off. Therefore, in 8 data disk
RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
the request) the aggregate performance is about 1.12
GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
there are no caches along the I/O path.  With the caches turned on, especially
the write-back cache on the DDN RAID controller, we observe a significant
performance improvement. In our day-to-day HPC operations we run our storage
systems with write-back cache turned on on RAID controllers, if and only if,
there is a method of cache-mirroring between the two active-active RAID
controllers. With the write-back cache on we observe \textasciitilde1.4 GB/s
per RAID 6 8+2 SAS group and  \textasciitilde955 MB/s per RAID 6 8+2 SATA
group, for 1 MB sequential I/O.  These two performance numbers will be used as
a baseline in our study and they are presented in
Table~\ref{tbl:block-io-baseline}.  For these tests, the 8+2 RAID 6 groups are
exported to the server hosts using SCSI RDMA Protocol (SRP) over IB protocol
(which is the default for our normal HPC configurations). For a SATA disk group
this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
MB/s/disk. As can be seen, SATA RAID groups benefit from caching more than SAS
groups.

>>>>

The lowest layer in the system are the exposed LUNs to the server hosts from
the RAID controllers.  These LUNs are configured as a RAID 6 8+2 array (8 data
disks and 2 \textit{P} and \textit{Q} disks).

In prior tests we observed
that a 7.2K RPM SAS disk can perform at 140 MB/s for 128 kB
sequential I/O requests and a 7.2K RPM SATA disk can do 36 MB/s.
For these tests, all disk caches were turned off. Therefore, in 8 data disk
RAID group with 1 MB sequential I/O requests (each disks sees 128 kB chunks of
the request) the aggregate performance is about 1.12
GB/s for a SAS RAID group and 288 MB/s for a SATA RAID group, if
there are no caches along the I/O path.  With the caches turned on, especially
the write-back cache on the DDN RAID controller, we observe a significant
performance improvement.

In our day-to-day HPC operations, we run our storage
systems with write-back cache turned on on RAID controllers, if and only if,
there is a method of cache-mirroring between the two active-active RAID
controllers. With the write-back cache on we observe \string~1.4 GB/s
per RAID 6 8+2 SAS group and  \string~955 MB/s per RAID 6 8+2 SATA
group, for 1 MB sequential I/O.  These two performance numbers will be used as
a baseline in our study and they are presented in
Table~\ref{tbl:block-io-baseline}.  For these tests, the 8+2 RAID 6 groups are
exported to the server hosts using SCSI RDMA Protocol (SRP) over IB protocol
(which is the default for our normal HPC configurations). For a SATA disk group
this translates into roughly 120 MB/s/disk and for a SAS disk group it is 175
MB/s/disk.

%As can be seen, SATA RAID groups benefit from caching more than SAS
%groups.
